Future Cosmic Microwave Background delensing with galaxies surveys.

### 2017-06-07 Notes/DES_rec_phi_paper.tex
text

We can also write the galaxy overdensity field $g(\nver)$ in a given direction on the sky as a line of sight integral of the matter overdensity:
\begin{equation}
g(\nver) = \int_0^{z_*} dz\, W^{g}(z)\delta(\chi(z)\nver,z),
\end{equation}
where the kernel is
\begin{equation}
\label{eqn:wg}
\begin{split}
W^{g}(z) &= \frac{b(z)\frac{dN}{dz}}{\Bigl(\int dz'\,\frac{dN}{dz'}\Bigr)}.
\end{split}
\end{equation}
Here $\frac{dN}{dz}$ is the number of galaxies as a function of redshift observed by the survey while $b(z)$ is the galaxy bias that connects the amplitude of galaxies overdensity to the one of the dark matter at different redshift.
When computing the auto-spectrum of a galaxies density, a shot noise term needs to be taken into account. 
To do so, we add a constant term to the power spectrum equal to the inverse of the number of galaxies per steradians.

@@

The correlation attainable using generation 3 experiments is shown in \reffig{corrS3}.
Not only will CMB experiments improved shortly: eventually  D.E.S.I will start taking data. For this reason, we add DESI to the previously mentioned LSS tracers. 
DESI will be slightly more efficient than DES-like survey because of the slightly higher redshift that it can probe.
However, the CIB will still play the major role among LSS.

>>>>

We can also write the galaxy overdensity field in a given direction on the sky as a line of sight integral of the matter overdensity.
The galaxies kernel is:
\begin{equation}
\label{eqn:wg}
\begin{split}
W^{g}(z) &= \frac{b(z)\frac{dN}{dz}}{\Bigl(\int dz'\,\frac{dN}{dz'}\Bigr)}.
\end{split}
\end{equation}
Here $\frac{dN}{dz}$ is the number of galaxies as a function of redshift observed by the survey while $b(z)$ is the galaxy bias that connects the amplitude of galaxies overdensity to the one of the dark matter at different redshift.
When computing the auto-spectrum of a galaxies density, a shot noise term needs to be taken into account. 
To do so, we add a constant term to the power spectrum equal to the inverse of the number of galaxies per steradians.

@@

The correlation attainable using generation 3 experiments is shown in \reffig{corrS3}.
Not only will CMB experiments improved shortly: eventually  DESI will start taking data. For this reason, we add DESI to the previously mentioned LSS tracers. 
DESI will be slightly more efficient than DES-like survey because of the slightly higher redshift that it can probe.
However, the CIB will still play the major role among LSS.
